Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-21 supp/supp.qmd
supp

A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server. Unsurprisingly, countries in North America and Europe use preprints more exstensively. Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* for their preprints (@fig-countries). Overall, 90% of the preprints come from `r nrow(most_use)-1` countries (@tbl-countries).

@@

>>>>

A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server. Unsurprisingly, countries in North America and Europe use preprints more exstensively. Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* for their preprints (@fig-countries). Overall, 90% of the preprints come from just `r nrow(most_use)-1` countries (@tbl-countries).

@@

## Taxa studied in preprints

```{r, taxa}
cols <- c("plants", "algi", "fungi", "microorganisms", "invertebrates", "vertebrates")

# Summary of the data
sum_taxa <- data2  %>% select(all_of(cols))  %>% apply(., 2, sum, na.rm = TRUE)  %>% data.frame()   %>% rownames_to_column(var = "taxa")  %>% rename("n" = ".")

blank_theme <- theme_minimal()+
  theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=14, face="bold")
  )

# Use data to create a pir chart and clean up colour palette

pie <- sum_taxa  %>% ggplot(aes(x = "", y = n, fill = taxa)) + geom_bar(stat = "identity") + coord_polar("y", start=0) + blank_theme + labs(title = "Taxa studied in preprints") + theme(legend.position = "bottom")
